\chapter{\abstractname}
In recent years, research and development in Internet of Things, pervasive computing and machine-to-machine communication have been trending in the computer science field alongside the evolution of wireless sensor networks and single board computers. 
This has  motivated researchers and developers to harness the power of combining intelligent agents capable of acting on their own with small computer devices, in order to enhance the  life quality of human beings, preserve the environment, improve the manufacturing  process and provide better health care. As a result, the usage of networking concepts such as Information-Centric, Delay-Tolerant architectures and publish-subscribe messaging systems has nurtured in order to provide efficient machine communication mechanisms to smart devices. Despite the increase of pervasive use cases, there is still a lack of frameworks that facilitate the distribution and harmonization of pervasive use cases. A framework that would assist in designing and deploying different use cases to edge devices in a network and allows communication and data sharing between them.  Therefore, we propose a software framework for distributing flows which are representations of computations describing use cases to smart devices in a network. The framework also takes care of the flows dependencies, resources, data communication, service discovery, delivering computations and data to challenged networks. It relies on the concepts of pervasive computing, information-centric and delay-tolerant networking. The framework also allows having inter-relationships between flows either locally on the same device or globally across different devices. The framework can help researches, industries and individuals to design and distribute computations to smart devices using flow-based programming with minimal amount of code.